\section{Related Work}
\paragraph{Tracking-by-detection baselines.}
Tracking-by-detection remains the dominant paradigm for online MOT. SORT \cite{bewley2016sort} and DeepSORT \cite{wojke2017deepsort} established the standard motion-plus-appearance recipe, while ByteTrack \cite{zhang2021bytetrack} showed that careful association over both high- and low-confidence detections is crucial for strong performance. OC-SORT \cite{cao2022ocsort} improved motion handling by emphasizing observation-centric updates. BoT-SORT \cite{aharon2022botsort} and StrongSORT \cite{du2022strongsort} further strengthened this family with better motion modeling, camera-motion compensation, and stronger ReID features.

\paragraph{Association refinement and appearance usage.}
Recent works increasingly focus on \emph{how} appearance should be used rather than simply \emph{whether} appearance should be used. Deep-OC-SORT \cite{maggiolino2023deepocsort} adaptively integrates ReID cues into a strong motion-based tracker. DeconfuseTrack \cite{huang2024deconfusetrack} explicitly addresses confusion in association by decomposing ambiguous matching cases and introducing targeted modules. These works reinforce a key insight: the main remaining gap in strong online MOT systems is often not raw detection, but robust association under ambiguity. Our work shares this focus but takes a different route. Instead of redesigning the tracker around adaptive appearance extraction or confusion decomposition, we ask a narrower and more transferable question: \emph{can we estimate the reliability of appearance matching from temporal signatures of a track's history?}

\paragraph{Temporal aggregation for appearance.}
Historical appearance features are often maintained through moving averages or smoothed track embeddings. Such summaries are useful, but they do not directly quantify whether the present observation is trustworthy. Our method uses multiple exponentially decayed prototypes to probe temporal consistency at different scales and explicitly converts that consistency into a reliability signal for association.

\paragraph{Plug-in MOT modules.}
Plug-in improvements are especially attractive for MOT because they can be evaluated fairly under fixed detectors and fixed trackers. ByteTrack \cite{zhang2021bytetrack}, StrongSORT \cite{du2022strongsort}, and DeconfuseTrack \cite{huang2024deconfusetrack} all highlight how association-centric design choices can transfer across trackers or benchmark settings. We follow this philosophy and design LTRA as a minimal intervention in the association stage of a standard tracker, rather than as a new end-to-end architecture.
